Decisions Decisions Decisions: Carrying out Latent Profile Analysis in Accordance With Best Practices Using the tidyLPA R package

### 2020-10-12 paper.rmd
update article

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
library(tidyverse)
knitr::clean_cache()
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

@@

``` {r, curry-mac-mclust-example}
m1 <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(1:10)
```

@@

```{r, eval = FALSE}
write_rds(compare_solutions_mclust, "compare_solutions_mclust.rds")
````

@@

```{r, echo = FALSE}
t <- read_csv("GRoLTS-applicability-to-LPA.csv")
tp <- t %>% 
  filter(use == 1) %>% 
  mutate(`LPA Number` = 1:nrow(.)) %>% 
  select(`GRoLTS Number` = Number, `LPA Number`, `Checklist Item`)

>>>>

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
library(tidyverse)
knitr::clean_cache()
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, warning = FALSE)
```

@@

Note that here and throughout this paper we use the function `knitr::kable()` to format the output in an RMarkdown document, like the one we are using; this is not necessary to use unless you also wish to format the tidyLPA output in an RMarkdown document.

``` {r, curry-mac-mclust-example}
m1 <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(1:10) %>% 
  knitr::kable()
```

@@

```{r, eval = TRUE}
write_rds(compare_solutions_mclust, "compare_solutions_mclust.rds")
````

@@

```{r, echo = FALSE}
t <- read_csv("GRoLTS-applicability-to-LPA.csv")

tp <- t %>% 
  filter(use == 1) %>% 
  mutate(`LPA Number` = 1:nrow(.)) %>% 
  select(`GRoLTS Number` = Number, `LPA Number`, `Checklist Item`)
